---
title: 'The Characters: Wives, Widows, Workers'
output: html_document
bookToC: true
weight: 50
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse) 
library(readxl)
library(plotly)
library(scales)
library(RColorBrewer)
contracts <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/contracts_gender_r_2.xlsx")
defs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/defs_r.xlsx")
plfs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/plfs_r.xlsx")
parties <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/parties_r.xlsx")
cites <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/cites_for_contracts.xlsx")
gendertotaltable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/gendertotaltable.xlsx")
partnertable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/partner_table.xlsx")

names(gendertotaltable)[1] <- "gender"
names(gendertotaltable)[5] <- "percentage"
opts <- options(knitr.kable.NA = "")

parties <- parties %>%
  full_join(cites)
names(parties)[4] <- "name"
contracts <- contracts %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

names(parties)[9] <- "cite"

n_parties_joiner <- parties %>%
  group_by(cite) %>%
  count() %>%
  mutate(n_parties = n) %>%
  select(cite, n_parties)

parties <- parties %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

contracts <- contracts %>%
  full_join(n_parties_joiner)

```

# The Characters

## Overall Gender Breakdown 

Here again is a table with general gender breakdown, with some additional information about plaintiff/defendant status. 

```{r, echo = FALSE, warning = FALSE, message = FALSE}

gendertotaltable %>%
  knitr::kable()
```

This is the same information in bar chart form for easier visualization.

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5,fig.height = 4}
gender_breakdown_with_pd <- parties %>%
  filter(typenomf == "Man" | typenomf == "Woman" | typenomf == "Unknown") %>%
  group_by(typenomf) %>%
  mutate(gendercount = n()) %>%
  ungroup() %>%
  group_by(typenomf, side) %>%
  mutate(gendersidecount = n()) %>%
  mutate(prop = gendersidecount/gendercount) %>%
  mutate(prop = as.character(prop)) %>%
  mutate(prop = str_sub(prop,3,4)) %>%
  mutate(prop = paste(sep = "",prop,"%")) 

gender_breakdown_with_pd[gender_breakdown_with_pd == "5%"] <- "50%"

gender_breakdown_with_pd <- gender_breakdown_with_pd %>%
  ggplot +
  geom_bar(aes(typenomf, fill = side, text = paste(sep = "",gendersidecount,", ",prop))) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Gender Breakdown with π/∆ status", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(gender_breakdown_with_pd, tooltip = "text")


```

Interestingly, women are more likely to appear on the plaintiff side than are men. This is not a significant difference and may not reflect anything meaningful, but it's an interesting side note. 


## Transaction Type Gender Breakdown

I coded for five rough types of transactions that give rise to the dispute being litigated. See the ["Data Collection and Dataset"](/docs/dataset) tab for an explanation of the types. 

I list in descending order of gender equity. 

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5,fig.height = 4}
parties_property <- parties %>%
  filter(transaction == "Property", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/37) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Property Transaction ", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_property, tooltip = "text")

```


```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5,fig.height = 4}
parties_family <- parties %>%
  filter(transaction == "Family", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/24) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Interpersonal Transaction", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_family, tooltip = "text")

```


```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5,fig.height = 4}
parties_consumer <- parties %>%
  filter(transaction == "Consumer", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/29) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Consumer Transaction ", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_consumer, tooltip = "text")

```

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5,fig.height = 4}
parties_employee <- parties %>%
  filter(transaction == "Employee", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/31) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Employee-Business Transaction ", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_employee, tooltip = "text")
```



```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5,fig.height = 4}
parties_business <- parties %>%
  filter(transaction == "Business", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/70) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Business-Business Transaction ", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_business, tooltip = "text")
```



