---
title: "Wives"
weight: 51
bookFlatSection: false
output:
  html_document: 
    css: columns.css
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse) 
library(readxl)
library(plotly) 
library(scales)
library(RColorBrewer)
library(kableExtra)
contracts <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/contracts_gender_r_2.xlsx")
defs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/defs_r.xlsx")
plfs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/plfs_r.xlsx")
parties <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/parties_r.xlsx")
cites <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/cites_for_contracts.xlsx")
gendertotaltable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/gendertotaltable.xlsx")
partnertable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/partner_table.xlsx")
couples <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/couples.xlsx")

names(gendertotaltable)[1] <- "gender"
names(gendertotaltable)[5] <- "percentage"
opts <- options(knitr.kable.NA = "")

parties <- parties %>%
  full_join(cites)
names(parties)[4] <- "name"
contracts <- contracts %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

names(parties)[9] <- "cite"

n_parties_joiner <- parties %>%
  group_by(cite) %>%
  count() %>%
  mutate(n_parties = n) %>%
  select(cite, n_parties)

parties <- parties %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

contracts <- contracts %>%
  full_join(n_parties_joiner)

parties[parties == "Government"] <- "Organization"
contracts[contracts == "Government"] <- "Organization"
```


## Marriage and Family 

Women in KCP are vastly, vastly more likely than men or individuals of unknown gender to appear in litigation with a heterosexual partner or a family member. Even discounting miscellaneous family status, a **majority - 56% - ** of women appearing in KCP appear with heterosexual partners. **70%** of women appear with a partner or family member. So only **30% of women in KCP - less than a third!! - appear independent of a relative.** In contrast, 70% of men and 100% of individuals of unknown gender appear independent of a relative. 


```{r, echo = FALSE, warning = FALSE, message = FALSE}
names(partnertable) <- c("","partner","%partner","family","%family","partner+family","%p+f")
partnertable %>%
  kbl()

```

Here is the same information in chart form for easier visualization. 

*You can scroll around the chart - each colored bar has the number of cases and the percentage of each gender's cases (*not all cases*) that it represents.* 

```{r, echo = FALSE, warning = FALSE, message = FALSE}

a <- parties %>%
  filter(typenomf == "Man" | typenomf == "Woman" | typenomf == "Unknown" ) %>%
  group_by(typenomf) %>%
  mutate(typea = n()) %>%
  ungroup() %>%
  group_by(typenomf,spouse) %>%
  mutate(typeb = n()) %>%
  mutate(percentage = paste(sep = "", str_sub(as.character(typeb/typea),3,4),"%"))
a[a == "%"] <- "100%"
a[a == "F"] <- "Misc. Family"
a[a == "N"] <- "Unrelated"
a[a == "Y"] <- "Spouse/Partner"
a <- a %>%
  arrange(spouse) %>%
  ggplot(aes(typenomf, fill = spouse)) + 
  geom_bar(aes(text = paste(sep = "", typeb,", ",percentage))) +
  labs(title = "Individuals by Gender and Family/Spousal Status", x = "Gender", y = "Number") +
  scale_fill_brewer(palette = "Accent", name = "Spousal/Family Status")
ggplotly(a,tooltip = "text")

```

## Little Discernable Change over Time? 

The following charts are split by gender and show each individual litigant who appears, colored by their spousal/family status. You can hover over the dots to see the name of the individual and the case in which they appear. If you double-click on any of the colored dots in the legend, the chart will isolate that category. 

I don't discern any particularly interesting trends over time, but you might disagree. 

*You can scroll around the chart - each dot has the name and year of the woman it represents.
All cases are randomly dispersed along the y axis to make the individual points easier to see. Vertical position is arbitrary.
Double-click on the colored dots within the legend/key to isolate that category.*

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=8,fig.height = 3}
woman_parties <- parties

woman_parties[woman_parties == "F"] <- "Misc. Family"
woman_parties[woman_parties == "N"] <- "Unrelated"
woman_parties[woman_parties == "Y"] <- "Spouse/Partner"
woman_parties <- woman_parties %>%
  filter(typenomf == "Woman") %>%
  group_by(name) %>%
  mutate(n = n()) %>%
  ggplot(aes(year,n, color = spouse, text = paste(sep = "", name,", ",side,", ",simplecite))) +
  geom_point(alpha = 0.3, size = 1.5, position = position_jitter(w = 0, h = 0.3)) +
  labs(title = "All Women as Parties") +
  scale_color_manual(values=c("red","blue","forestgreen"),name = "Spousal/Family Status", labels = c("Misc. Family","Unrelated","Spouse/Partner"))
  
ggplotly(woman_parties, tooltip = "text") 
```


*You can scroll around the chart - each dot has the name and year of the man it represents.
All cases are randomly dispersed along the y axis to make the individual points easier to see. Vertical position is arbitrary.
Double-click on the colored dots within the legend/key to isolate that category.*

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=8,fig.height = 3}
man_parties <- parties

man_parties[man_parties == "F"] <- "Misc. Family"
man_parties[man_parties == "N"] <- "Unrelated"
man_parties[man_parties == "Y"] <- "Spouse/Partner"

man_parties <- man_parties %>%
  filter(typenomf == "Man") %>%
  group_by(name) %>%
  mutate(n = as.integer(n())) %>%
  ggplot(aes(year,n, color = spouse, text = paste(sep = "", name,", ",side,", ",simplecite))) +
  geom_point(alpha = 0.3, size = 1.5, position = position_jitter(w = 0, h = 0.3)) +
  labs(title = "All Men as Parties") +
  scale_color_manual(values=c("red","blue","forestgreen"),name = "Spousal/Family Status") +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())

ggplotly(man_parties, tooltip = "text") 

```

### Complicated graph but you can figure it out if you play with the legend - double-click the dot/square/triangle to isolate

#### Men are circles, women are squares, unknowns are triangle
#### Red is miscellaneous family, blue is spouse/partner, green is unrelated individual


```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=8,fig.height = 3}
all_parties <- parties

all_parties[all_parties == "F"] <- "Misc. Family"
all_parties[all_parties == "N"] <- "Unrelated"
all_parties[all_parties == "Y"] <- "Spouse/Partner"
all_parties <- all_parties %>%
  filter(typenomf == "Woman" | typenomf == "Man" | typenomf == "Unknown") %>%
  group_by(name) %>%
  mutate(n = n()) %>%
  ggplot(aes(year,n, color = spouse, shape = typenomf, text = paste(sep = "", name,", ",side,", ",simplecite))) +
  geom_point(alpha = 0.3, size = 1.5, position = position_jitter(w = 0, h = 0.3)) +
  labs(title = "All Parties: Men are Circles, Women Triangles") +
  scale_color_manual(values=c("red","blue","forestgreen"),name = "Spousal/Family Status", labels = c("Misc. Family","Unrelated","Spouse/Partner"))
  
ggplotly(all_parties, tooltip = "text") 
```

## The (Un)Happy Couples 

Most of the spouses/partners are members of one of the 24 couples who appeared with or against a heterosexual partner in a relationship. 


```{r, echo = FALSE, warning = FALSE, message = FALSE}
partnertable %>%
  knitr::kable() 
couples1 <- couples %>%
  filter(couple == 1)
couples2 <- couples %>%
  filter(couple ==2)
couples3 <- couples %>%
  filter(couple == 3)
couples4 <- couples %>%
  filter(couple ==4)

couples_table <- couples1 %>%
  right_join(couples2,by=c("page","year","transaction","cite","simplecite")) %>%
  select(name.x,name.y,page,simplecite)

couples_table2 <- couples3 %>% 
  right_join(couples4,by=c("page","year","transaction","cite","simplecite")) %>%
  select(name.x,name.y,page,simplecite)

couples_table <- full_join(couples_table, couples_table2)
names(couples_table) <- c("Partner 1", "Partner 2", "Page", "Cite")

kable(couples_table, "html", caption = "Couples in KCP") %>%
  kable_styling(fixed_thead = TRUE) %>%
  scroll_box(height = "300px") 


```

### Operating Together

Most of the couples appear on the same side of the litigation, operating essentially as a unit. Interestingly, most of [UNIFINISHED!!]

Many operate as a unit. Where one appears as a more prominent agent than the other, the more prominent one is most often a man. 

### The Adversaries
[UNFINISHED!!]

These involve the difficulty of heterosexual relationships. The Watts case and the Chen case are about the conflict resulting from separation, while the surrogacy case is about the conflict resulting from a deviation from the norm of a *man* and a *woman* having *natural children.*

## Relevant Non-Party Spouses

Two men and two women had their relationships described with reference to the proceedings but without their partner appearing.


#### *Locke v. Warner Bros., Inc.*
##### 57 Cal. App. 4th 354 (1997); KCP 513

Sondra Locke’s dispute with Warner Bros. is framed as something patronizingly set up for her by her ex Clint Eastwood (not a party), relevant to the argument about good faith.

#### *King v. Trustees of Boston Univ.*
##### 420 Mass. 52 (1995); KCP 237

Coretta Scott King brings her case on behalf of her family estate, and is actually a great example of rhetoric relating a woman to a husband but still giving her full agency: 
> *“The plaintiff, Coretta Scott King, in her capacity as administratix of the estate of her late husband, and in her individual capacity, appeals...”*

#### *Katz v. Danny Dare Inc.*
##### 610 S.W.2d 121 (Mo. Ct. App. 1980); KCP 248

I.G. Katz brought a promissory estoppel claim against a company the president of which “was also the brother of Katz’s wife,” establishing the connection between Katz and the company; moreover, his wife would benefit from a Social Security clause in the promised contract.

#### *Credit Bureau Enter. v. Pelo*
##### 608 N.W.2d 20 (Iowa 2000); KCP 297

Russell N. Pelo was involuntarily committed to a hospital after he telephoned his wife to make threats of self harm, relevant to the context of his refusal to pay. 


## Barely Relevant Non-Party Spouses

One man and one woman had their marital status described as a strange, but seemingly purposeful, aside.  

#### *Dohrmann v. Swaney*
##### 14 N.E.3d 605 (Ill. 2014); KCP 129

This is one of the cases about a [vulnerable widow being taken advantage of](/docs/characters/characters3). The court affirmed a summary judgment that a contract between Virginia H. Rogers, offering over $5.5 million in assets upon her death, and George Dohrmann, promising to add Rogers as a middle name for both of his sons, was unenforceable because the consideration was illusory (and "so grossly adequate as to shock the conscience.") 

Dohrmann is first introduced merely as "the appellant" and Rogers as "deceased (The Estate). The next information revealed is that Dohrmann was Rogers' neighbor, and had minor children. The first robust introduction that Judge Fitzgerald Smith of the Illinois Appellate Court gave to the characters is as follows, in the "Background" section:

> At the time they met, Mrs. Rogers was 73-year-old widow. She had never had nor adopted any children. Dohrmann was a 40-year-old neurosurgeon, married to Dr. Helen Dohrmann. 

As I explore more thoroughly in the [widows section](/docs/characters/characters3), Mrs. Rogers' old age and husbandlessness play into a sense of vulnerability, which explicitly ties into the court's ruling of illusory consideration and dictum that the case could have been found void on the grounds of "unfairness" alone. The judge repeatedly mentions that Mrs. Rogers was not only old, but *also a widow,* harnessing general cultural assumptions about vulnerability to bolster their argument. 

What value does the inclusion of Dohrmann's job, his marriage, and his wife's job add to the opinion? Perhaps Dohrmann's marital status establishes that he was not as sad and lonely as Rogers is implied to be, or merely to contextualize his having children. The more interesting tidbit is the inclusion of both of their jobs. Simply in terms of gender representation, a side mention as "Dr. Helen Dohrmann" implies status, power, and wealth not usually associated with women. But it's unlikely that Judge Fitzgerald Smith's goal was to subtly challenge gender stereotypes. Perhaps the occupations establish that the Dohrmanns were well off, ruling out any moral defense based on need. 


#### *Aceves v. U.S. Bank N.A.*
#### 120 Cal. Rptr. 3d 507 (Cal. Ct. App. 2011); KCP 255

In Aceves v. U.S. Bank, N.A. the judge present the plaintiff, a woman independently bringing a suit whose spouse appears only as a minor detail in the rest of the opinion, as “Claudia Aceves, a married woman.” (255) The case is about bankruptcy – perhaps her marriage establishes some kind of moral credibility? There might be some kind of difference in the judge's mind between a bankrupted single woman and a bankrupted wife. 