---
title: "Workers"
output: html_document
weight: 53
bookFlatSection: false
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(tidyverse) 
library(readxl)
library(plotly)
library(scales)
library(RColorBrewer)
library(kableExtra)
contracts <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/contracts_gender_r_2.xlsx")
defs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/defs_r.xlsx")
plfs <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/plfs_r.xlsx")
parties <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/parties_r.xlsx")
cites <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/cites_for_contracts.xlsx")
gendertotaltable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/gendertotaltable.xlsx")
partnertable <- read_excel("/Users/professorserrano/Desktop/Documents/Video Essays/Law/partner_table.xlsx")

names(gendertotaltable)[1] <- "gender"
names(gendertotaltable)[5] <- "percentage"
opts <- options(knitr.kable.NA = "")

parties <- parties %>%
  full_join(cites)
names(parties)[4] <- "name"

contracts <- contracts %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

names(parties)[9] <- "cite"

n_parties_joiner <- parties %>%
  group_by(cite) %>%
  count() %>%
  mutate(n_parties = n) %>%
  select(cite, n_parties)

parties <- parties %>%
  mutate(simplecite = cite) %>%
  mutate(simplecite = str_extract(simplecite, "[^,]+"))

contracts <- contracts %>%
  full_join(n_parties_joiner)

parties[parties == "Government"] <- "Organization"
contracts[contracts == "Government"] <- "Organization" 

```

Characters: Workers 

Recall from the [first character page](/docs/characters/_index) that Employee-Business and Business-Business transactions are the most male-skewed, at 82:18 and 83:17 splits respectively.  

## Employee Transactions

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height = 4}
parties_employee <- parties %>%
  filter(transaction == "Employee", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/31) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Employee-Business Transaction ", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_employee, tooltip = "text")
```

#### Employees: The Women

```{r, echo = FALSE, warning = FALSE, message = FALSE}
parties %>%
  filter(transaction == "Employee",typenomf == "Woman") %>%
  select(name, side, simplecite) %>%
  kbl() %>%
  scroll_box(fixed_thead = T, height = "300px") 
```

Half the women are on the plaintiff side, half on the defendant. Two of the women on the defendant side, Joannie Collins and Elizabeth Arden, are businesspeople representing organizations being sued by former employees. Elaine Lukaszewski is on the defendant side, but is a former employee being sued for breach of contract. The three plaintiff-side women are former (or potential) employees suing businesses for having breached their employment contracts.

#### Employees: The Men

```{r, echo = FALSE, warning = FALSE, message = FALSE}
parties %>%
  filter(transaction == "Employee",typenomf == "Man") %>%
  select(name, side, simplecite) %>%
  arrange(desc(name)) %>%
  arrange(side) %>%
  kbl() %>%
  scroll_box(fixed_thead = T, height = "300px") 
```

13 men are on the defendant side, 12 on the plaintiff side: essentially the same 50-50 split as the women. You may notice the "16 other people" - they never appear as real individual characters in the litigation but are gendered as men. 

#### Plowman v. Indian Refining Co.
##### 20 F. Supp. 1 (E.D. Ill. 1937)
##### KCP 120
> Thirteen persons and the administrators of five deceased persons brought this suit ... The general manger of the refinery plant called the employees, who had rendered long years of service into his office and made with each a contract, to pay **him**, for the rest of **his** natural life ... the Lawrenceville Refinery where **these men** were employed...

I took out and counted separately the people who appeared individually, such as "Plaintiff Kogan," but conglomerated the rest of the plaintiffs into one data point so they don't inflate the number of men. As the name of the section suggests, I'm more interested in the individuals who appear as characters, taking action and doing things, than all the parties who appear in litigation.

## Business Transactions

There's also a wealth of stuff to study here about class, labor, and bargaining power - the Alaska crabbers case comes to mind particularly strongly. However, I think that this type of inquiry in contract law is pretty well developed in comparison to gender- and race-based analyses. Much like with Russell Pelo and questions of mental health, I think this is a very interesting area for research that I won't do justice to in this project.  

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height = 4}
parties_business <- parties %>%
  filter(transaction == "Business", typenomf == "Man" | typenomf == "Woman") %>%
  group_by(typenomf) %>%
  mutate(n = n(), proportion = n/70) %>%
  mutate(proportion = as.character(proportion)) %>%
  mutate(proportion = substr(proportion, 1, 4))  %>%
  mutate(proportion = substr(proportion, 3, 4)) %>%
  mutate(proportion = paste(sep = "",proportion,"%")) %>%
  ggplot() +
  geom_bar(aes(typenomf,fill = typenomf,text = paste(sep = "", n,", ",proportion)),fill=c("thistle2","lightsteelblue2")) +
  labs(title = "Business-Business Transaction ", x = "Gender", y = "Count - Hover for N and %") +
  theme_bw()
ggplotly(parties_business, tooltip = "text")
```

#### Locke v. Warners Bros., Inc.
###### 57 Cal. App. 4th 354 (1997); KCP 513

Judge Klein of the California Court of Appeal's account of the dispute between Sondra Locke and Warner Bros. is remarkable for its simultaneous recognition and dismissal of gender bias in the workplace. The judge first contextualizes Locke's dispute as arising from a messy break-up with Clint Eastwood. They raise the issue of gender discrimination out of necessity in a brief section listing Locke's causes of action: 

> The first cause of action alleged sex discrimination in violation of public policy. Locke alleged Warner denied her the benefit of the bargain of the development deal on account of her gender. The third cause of action, captioned "Tortious Breach of the Implied Covenant of Good Faith and Fair Dealing in Violation of Public Policy," alleged a similar claim. Locke pled that in denying her the benefits of the Warner/Locke agreement, Warner was "motivated by [its] discriminatory bias against women in violation of ... public policy." 

Gender discrimination gets a brief one-sentence mention at the end of the section on the trial court's ruling: 

> As for the two causes if action alleging sex discrimination, the trial court found no evidence Warner declined to develop the projects Locke submitted, and declined to use her directing services, on account of her gender. 

The opinion then presents strong evidence of a triable issue of fact regarding Warner Bros. lack of good faith for several pages without any specific discussion of gender. Gender comes up one last time near the end:

> 4. "Locke Waived any Error in the Trial Court's Ruling with Respect to Her Causes of Action Alleging Gender Bias" 

The section is a cursory two paragraphs describing Locke's failure to properly raise the issue of the trial court's finding of no sex discrimination in a timely manner. It does not address the substance of her claims at all. 

Overall, Judge Klein seems to duck the issue of gender as much as possible. 

Interestingly, I'm pretty sure that the Judge Klein on the California Court of Appeals in 1997 was [Joan Dempsey Klein](https://www.latimes.com/california/story/2021-01-03/justice-joan-dempsey-klein-obituary), described as a "celebrated champion of women's rights." I think this is an example of an activist choosing her battles. There are times and places that are strategically optimal for pushing a progressive agenda, and times and places that are not. The messy personal tea of a famous actress is not exactly the ideal case to point out systemic issues.

#### KCP's Note 3: Gender of racial discrimination as a breach of duty of good faith

This is one of best and most fleshed-out conversations about identity-based discrimination that KCP include in the casebook.  It is one of the longer notes in the book, taking up about a full page. 

#### Businesspeople: The Women

```{r, echo = FALSE, warning = FALSE, message = FALSE}
parties %>%
  filter(transaction == "Business",typenomf == "Woman") %>%
  select(name, side, simplecite) %>%
  kbl() %>%
  scroll_box(fixed_thead = T, height = "200px") 
```

#### Businesspeople: The Men

```{r, echo = FALSE, warning = FALSE, message = FALSE}
parties %>%
  filter(transaction == "Business",typenomf == "Man") %>%
  select(name, side, simplecite) %>%
  kbl() %>%
  scroll_box(fixed_thead = T, height = "300px") 
```
